Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?

### 2022-09-24 SIOP2023/Counts/Submission_ResourceCount.Rmd
Alicia graph auto-number generate (added fig.cap)

```{r matchpercentsbyperson}
#rc1 to rc 84

@@

#This should be matches divided by 84 items minus nas
data$percent_match_total_person <- (data$match_rc_by_person/(84 - data$match_rc_by_person_NAs))
head(data$percent_match_total_person)

>>>>

```{r matchpercentsbyperson, fig.cap="Distribution of the proportion of matches by person."}
#rc1 to rc 84

@@

#This should be matches divided by 84 items minus nas
data$percent_match_total_person <- (data$match_rc_by_person/(84 - data$match_rc_by_person_NAs))
# head(data$percent_match_total_person)
